Cosmology with photometric weak lensing surveys: constraints with redshift tomography of convergence peaks and moments

### 2016-05-03 photoz_paper/paper.tex
use eps instead of pdf

\begin{figure}
\includegraphics[scale=0.3]{Figures/galdistr.pdf}
\caption{Galaxy distribution assumed throughout this work (see equation (\ref{meth:galdistr})), along with the choice of the redshift bins $\bar{z}_b$. Our galaxy sample consists of $N_g=10^6$ galaxies. The figure shows the number of galaxies $N_g(z)$ at each redshift $z$.}
\label{fig:galdistr}
\end{figure}

@@

\begin{figure*}
\includegraphics[scale=0.3]{Figures/w_power_spectrum_no_pca.pdf}
\includegraphics[scale=0.3]{Figures/w_peaks_no_pca.pdf}
\includegraphics[scale=0.3]{Figures/w_moments_no_pca.pdf}
\caption{Comparison between single-redshift $w$ constraints (marginalized over $\Omega_m$ and $\sigma_8$) obtained without PCA (gray shaded bars) and with PCA (colored bars) as a function of the redshift bin $\bar{z}_b$. We show constraints obtained from the power spectrum (top left), peak counts (top right) and moments (bottom). Note the different scales on the vertical axis in the three different panels. The black dashed lines in the top left panel refer to parameter constraints on $w$ obtained with the public code NICAEA \citep{Nicaea}, assuming a Gaussian covariance model for the power spectrum, as specified by equation (\ref{meth:gausspcov}).}
\label{fig:nopca}
\end{figure*}

>>>>

\begin{figure}
\includegraphics[scale=0.3]{Figures/galdistr.eps}
\caption{Galaxy distribution assumed throughout this work (see equation (\ref{meth:galdistr})), along with the choice of the redshift bins $\bar{z}_b$. Our galaxy sample consists of $N_g=10^6$ galaxies. The figure shows the number of galaxies $N_g(z)$ at each redshift $z$.}
\label{fig:galdistr}
\end{figure}

@@

\begin{figure*}
\includegraphics[scale=0.3]{Figures/w_power_spectrum_no_pca.eps}
\includegraphics[scale=0.3]{Figures/w_peaks_no_pca.eps}
\includegraphics[scale=0.3]{Figures/w_moments_no_pca.eps}
\caption{Comparison between single-redshift $w$ constraints (marginalized over $\Omega_m$ and $\sigma_8$) obtained without PCA (black bars) and with PCA (colored bars) as a function of the redshift bin $\bar{z}_b$. We show constraints obtained from the power spectrum (top left), peak counts (top right) and moments (bottom). Note the different scales on the vertical axis in the three different panels. The black dashed lines in the top left panel refer to parameter constraints on $w$ obtained with the public code NICAEA \citep{Nicaea}, assuming a Gaussian covariance model for the power spectrum, as specified by equation (\ref{meth:gausspcov}).}
\label{fig:nopca}
\end{figure*}
